{\it Proposal:}\\ Ultrashort pulsed microwave viral envelope disruption as a COVID-19 treatment

### 2020-09-17 documents/distribution.tex
test

@@

\cite{Microwave2009} already mention this effect; \cite{Elastic} does a much better analysis than we do.

@@

This problem has a long history, stretching back to Cole-Cole's landmark paper in 1942\cite{Dispersion1941} and \cite{Electrical1941}.

@@

Worse still, influenza exhibits pleiomorphy \cite{Influenza2006};

NCoV is closer to \cite{Viral2020}, but does not exhibit pleiomorphy.

A cursory fit found parameters $\bar{\text{Q}}$=3.736,  $\sigma \ \text{Q} = $0.738, $\bar{F}_{res}=$8.606 GHz and $\sigma {F_{res}}=$1.073 and covariance of +1.001. This describes the observed spectrum equally well:

@@

@@

Since this entire covariance process will have to be repeated for SARS-NCoV-2 - that is, the CoV for NCoV, we have not bothered to fine-tune any of these fits. This must still be regarded as only a speculative hypothesis.

However, it offers a slight optimization: rather than applying a pulse of a single frequency, the pulses should be swept across the frequency distribution. From the (extremely crude) approximations on Inf. A above, this has little effect on $<$ 90-th percentile virions, but decreases the inactivation field of the last 10\% by perhaps 50 V/m.

@@

In the case of patch antennas for phased arrays, U-slots have to be added to dull the impedance bandwidth; all sorts of free-space injection-locking techniques become untenable; waveguide applicators start to run into overlapping transmission modes.

@@

\begin{center}
	\begin{tabular}{||c c c c||} 
		\hline
		Col1 & Col2 & Col2 & Col3 \\ [0.5ex] 
		\hline\hline
		1 & 6 & 87837 & 787 \\ 
		\hline
		2 & 7 & 78 & 5415 \\
		\hline
		3 & 545 & 778 & 7507 \\
		\hline
		4 & 545 & 18744 & 7560 \\
		\hline
		5 & 88 & 788 & 6344 \\ [1ex] 
		\hline
	\end{tabular}
\end{center}

>>>>

\begin{center}
	{\bf \cite{Microwave2009} already mention this effect; \cite{Elastic} does a much better analysis than we do.}
\end{center}

@@

@@

This problem has a long history, stretching back to Cole-Cole's landmark 1942\cite{Dispersion1941} paper and \cite{Electrical1941}. Such concerning statements as 'mathematically ill-posed' are bandied about; however, standard optimization techniques work fine.

@@

Worse still, influenza exhibits pleiomorphy, stretching into a variety of \cite{Influenza2006};

NCoV is closer to \cite{Viral2020}, but does not appear to exhibit pleiomorphy.

A cursory fit found parameters $\bar{\text{Q}}$=3.736,  $\sigma \ \text{Q} = $0.738, $\bar{F}_{res}=$8.606 GHz and $\sigma {F_{res}}=$1.073 \st{and covariance of +1.001}\footnote{warning}. This describes the observed spectrum equally well as Q=2.0:

@@

Since this entire covariance process will have to be repeated for SARS-NCoV-2 - that is, the CoV for NCoV, we have not bothered to fine-tune any of these fits; and so the idea that the Q-factor is higher than previously reported must still be regarded as only a speculative hypothesis.

@@

However, it offers a self-evident optimization: rather than applying a pulse of a single frequency, the pulses should be swept across the frequency distribution. From the (extremely crude) approximations on Inf. A above, this has little effect on $<$ 90-th percentile virions, but decreases the inactivation field of the last 10\% by perhaps 50 V/m.

@@

In the case of patch antennas for phased arrays, U-slots have to be added to dull the impedance bandwidth; all sorts of free-space injection-locking techniques become untenable; waveguides and cavities start to run into overlapping transmission modes. Structures like magnetron cavities are hard to

@@

Are such high pulse powers achievable?
